This is the Title

### 2017-05-11 paper/paper-DrexelFormat.tex
updated paper - abstract

\begin{abstract}
{\color{blue}[To do: Write an abstract here]}
\end{abstract}
\end{preamble}

@@

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.65\textwidth]{pictures/figures/RNN.png}
    \caption{RNN {\color{red} change variables}}
    \label{fig:RNN}
\end{figure}

>>>>

\begin{abstract}
{\color{blue}[To do: Review, 'This is the Title'?]}

The driving simulation data is popularly used for AI such as self-driving car. Children Hospital of Philadelphia (CHOP) is also interested on driving simulation data and AI to diagnose teenager's attention deficit/hyperactivity disorder (ADHD). The paper introduces to classification between expert and inexpert driver on given simulation data by using LSTM deep neural network. To deal with a few number of simulation data, cross validation is used and to deal with too densely sampled original data, the original is re-sampled. The paper also compares classifications between reduced dimension data by human and reduced dimension data by Auto-encoder.

\end{abstract}
\end{preamble}

@@

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.65\textwidth]{pictures/figures/RNN.png}
    \caption{RNN}
    \label{fig:RNN}
\end{figure}
